---
title: "dogma_package"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{dogma_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# The dogma.package

Github link: <https://github.com/rforbiodatascience25/group_24_package>

### Authors

Helena Utzon, S153655\@dtu.dk

Christian, s150251\@dtu.dk

Pernille

Lanjing

Inma

## Summary

The dogma package is a collection of functions which enables the user to create DNA sequences and manipulate these into RNA, codons, amino acids and fianlly, plot the accourance of each amino acid.

## Components

#### Data

#### Function 1

#### Function 2

#### function 3

#### Translation

The function takes a vector with codons (output from function 3)

#### Function 5: aa_plot

The function takes a string of amino acids (one letter abbreviations), counts the number of each amino acid, and generates a barplot showing the counts. The output of the function is the barplot. The function depends on the packages ggplot2 and stringr.

The function is performed by typing "aa_plot(data)" with data being a string of amino acids.

## 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dogma.package)
```
