---
title: "dogma_package"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{dogma_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r,setup}
library(dogma.package)
```

The Github link to the package can be found at [dogma.package](https://github.com/rforbiodatascience25/group_24_package).

## Summary

The dogma package is a collection of functions which enables the user to create DNA sequences and manipulate these into RNA, codons, amino acids and fianlly, plot the occurrence of each amino acid in barplot.

## Components

#### Data

The data used by the package includes a standard translation table for translating codons into amino acids.

#### Function 1

#### Function 2: dna_to_RNA

The dna_to_RNA() function converts a DNA sequence into an RNA sequence by replacing all T (thymine) with U (uracil), both uppercase and lowercase. It uses the gsub() function to make the substitutions and returns the transcribed RNA sequence.

```{r}

dna_to_RNA <- function(dna_sequence){
  rna_sequence <- gsub("T", "U", dna_sequence)
  rna_sequence <- gsub("t", "u", rna_sequence)
  return(rna_sequence)
}

```

#### Function 3: mRNA_to_codons

The function mRNA_to_codon takes RNA in a string as input to extract and replace with codons. The output of the function is a vector with multiple codons as strings seperated by ",".

##### **Example Usage**

```{r,message=FALSE}
mRNA <- "AUGUCG"
mRNA_to_codon(mRNA)
```

#### Function 4: Translation

The function takes a vector with RNA codons and translates the input into amino acids (one letter abreviations).

##### Example Usage

```{r}
codons <- c("UUU", "UAU", "AAA")
translation(codons)
```

#### Function 5: aa_plot

The function takes a string of amino acids (one letter abbreviations), counts the number of each amino acid, and generates a barplot showing the counts. The output of the function is the barplot. The function depends on the packages ggplot2 and stringr.

The function is performed by typing "aa_plot(data)" with data being a string of amino acids.
